Confidence Intervals for Prevalence Estimates from Complex Surveys with Imperfect Assays

### 2023-02-01 response_to_decision_letter.tex

\textbf{Response to Review for Manuscript Number: SIM-22-0426}

Title: "Confidence Intervals for Prevalence Estimates from Complex Surveys with Imperfect Assays"

We are grateful to the editor and reviewers for their thoughtful comments and the opportunity to improve and resubmit our manuscript.
Our response to individual comments from each reviewer follow.

\textbf{ Associate Editor}

Comments to Author:
\textbf{Your article has been thoroughly reviewed by an expert in the field. You will see that they have several suggestions and comments for you to address, and they see multiple contributions from the article.
As the reviewer suggests please ensure it is clear in the introduction what are the major research gap(s) the article addresses, and it is clear in the discussion what contribution(s) you believe the article has made.}

We have addressed the reviewers comments in detail below.
We have rewritten the abstract and expanded the first paragraph of the introduction to be clear about the research gaps this article addresses and to be clear about what is new in our article.
We have also rewritten the discussion to make our main contributions clear.

@@

\textbf{Reviewer: 1}
(There are no comments.)

\textbf{Reviewer 2}

\begin{itemize}
    \item \textbf{This paper has many strengths and yet could benefit from a revision that clarifies the main contribution(s) of the work. The new method is mathematically clever and appears to have the nice property of guaranteeing nominal CI coverage (though it is unclear if this has been rigorously proved); the contribution alone of generalizing the melded CI to more than 2 parameters is interesting, as well as the applicability of their method to complex surveys where each individual has their own weight. There was clearly painstaking detail taken in simulation studies to evaluate the new method.}

We have clarified our contributions (see answers below). 
We have also now explicitly stated in the first paragraph of the introduction that while our confidence interval is designed to guarantee coverage, there is no proof of that property given in the paper.
The conjecture of guaranteed coverage is supported by simulation only.

@@

    \item \textbf{The abstract and introduction imply that a main contribution of the work is that the new methods have better properties in simulations, and no drawbacks are hinted at. However, it is not clear that the new methods achieved better performance. Performance is strong at very low prevalences, but fades at higher prevalences. This is probably because the gamma CI method uses a Poisson approximation to the binomial that assumes a small binomial parameter, i.e., a small prevalence closer to 0 than 1.}

    \textbf{“our methods appear to guarantee coverage in simulated settings, while competing methods are shown to achieve much lower than nominal coverage” (Abstract).}

    \textbf{“we…show through simulations that [our new method] beats the best of [the established frequentist competitors] in each of the three stages **with respect to guaranteeing coverage**” (Introduction, last paragraph; emphasis added.) The three stages are (1) random samples with misclassification; (2) weighted samples without misclassification (using a perfect assay); and (3) weighted samples with misclassification.}

We have rewritten the introduction and discussion to be clear
that a main point of the paper is that there did not exist 
established methods for creating confidence intervals for prevalence estimates from complex surveys when the assays are imperfect.
Our paper has developed methods for that situation
(closely related to the Kalish, et al method, for which the properties were not fully studied), and studied the properties  of those methods.

In the special cases (e.g., simple random samples with imperfect 
assays, or complex samples with perfect assays), we could compare our method to established methods. 
    We have added some mentions in the text about the drawbacks to our proposed methods compared to the established ones and to clarify the scenarios when our methods are shown to be superior:

    \begin{description}
\item[    Abstract:]
    ``In some simulations, our methods appear to guarantee coverage, while competing methods have much lower than nominal coverage, especially when overall prevalence is very low. In other settings, our methods are shown to be overly conservative."

\item[    Introduction:]

@@

    ``However, in some simulated settings, our proposed methods are overly conservative, while competitor methods maintain closer to nominal coverage."

\item[    Discussion:]
    ``These new confidence intervals appear to guarantee coverage in most simulated settings, including some scenarios where competitor methods dramatically under-cover.
    In general, our methods demonstrate higher coverage than competitor methods in most scenarios, sometimes being very conservative while competitor methods demonstrate closer to nominal coverage.""
\end{description}

@@

    \item \textbf{The new method may guarantee coverage well, but it seems to do so by using conservative intervals that over-cover. Should such intervals be preferred to intervals that are more permissive (anti-conservative)?}

  First, we make the point again, that was not made clear enough in our previous version, that the new methods that we study in this paper (WprevSeSp Poisson and WprevSeSp Binomial)
do not have an established comparator method.
There are no previously established tractable methods to give confidence intervals for prevalence from complex surveys with imperfect assays.
(This is excluding valid methods that were developed recently and were not in print when we submitted, such as DiCiccio et al.
See remarks in our introduction about those recently developed methods).

For the special cases where there are alternative analyses (e.g., for a simple random sample with an imperfect assay, where we could use the method of Lang and Reiczigel), then the decision on which method to use would depend on the application.
If at least nominal coverage are important, and directional inferences are important (e.g., you want to know if the prevalence is larger than some value, so you are interested in the lower error of the confidence interval), then the new methods seem attractive.
If approximately nominal coverage for the two-sided interval is desired, then the method of Lang and Reiczigel may be recommended.

@@

    ``Figure~1 shows that, when specificity is less than perfect, the Lang-Reiczigel method achieves approximately nominal coverage, while the melding method is slightly more conservative, generally demonstrating 96\%-97\% coverage with 95\% confidence intervals."

    \item \textbf{(The discussion of lower and upper error probabilities in Section 3.1 is similar. The authors criticize the Lang-Reiczigel intervals for having “lower error above 2.5\%, which is undesirable…”. However, neither the lower nor upper errors of the melding method achieves nominal 2.5\% in any scenario. This is undesirable and unremarked upon. As a minor point, no reason for focusing on lower and upper error probabilities is stated; those Figures may be better relegated to the appendices.)}

    We have updated the text to motivate the figures and remark upon the undesirable lower error properties of the melding method:

    ``For a more nuanced depiction of each method's properties, we separate the overall coverage into lower and upper errors.
    Figure~3 shows that both methods make upper errors with roughly the same frequency.
    Figure~2 demonstrates that while the melding procedure bounds the lower error frequency below 2.5\%, the Lang-Reiczigel method generally has lower error above 2.5\%.
    Each of these behaviors may be undesirable, depending on the context in which the methods are applied.
    For applications in which there is a need to bound the lower errors, the melding method appears to be superior."

@@

    In our simulations, we did compare the wsPoisson method to the two melding methods, but the results were poor and made comparison between the melding methods more difficult to observe in the figures.
    We have clarified this point in the text.
    We have also noted the generally superior performance of the WprevSeSp Binomial method:

    ``In the other scenarios tested, the WprevSeSp Binomial generally achieves closer to nominal coverage than the WprevSeSp Poisson."

    \item \textbf{Is there a substantive reason that the prevalences assessed in simulations are 0.5\% and 5\%? While the number of scenarios evaluated are clearly substantial, it would be interesting to understand the methods’ performance across a larger portion of the [0, 1] prevalence parameter space.}

The simulation prevalence of 5\% is very close to the value from our motivating data example.
The 0.5\% was chosen as to see how well the method does for a much lower value. 
Although it would be interesting to study the performance across a larger portion of the prevalence parameter space, we leave that to future work because we already have an extensive set of simulation results in this paper.

In response to your comment, we have added a paragraph to the beginning of the simulation section and another paragraph in the discussion section to emphasize the limitation of the simulations with respect to prevalence values.

In the discussion we have added: ``Although this paper has done extensive simulations, the focus of the simulations was for low prevalence and high 
sensitivity and specificity. For other situations, especially high prevalence situations, more work is needed to more fully explore the properties of these methods.''

    \item \textbf{If the main contribution of the paper is superior coverage properties, then the above issues of the Poisson approximation assuming a small prevalence as well as simulation results and interpretation should be addressed. The authors could instead elaborate on other contributions of the work detailed above.}

    The main contribution of the paper is to have a confidence interval method that can be applied to complex surveys when there is also misclassification.
    Although Kalish {\it et al} 2021 (note: the second and third authors of the submitted paper were also authors on Kalish {\it et al}) did have a method that could be applied to that type of data, but since the focus of that paper was the results of the survey, it did not study the properties of that method.
    This paper is in some sense a companion paper to that paper, in that it can study the properties an interval very similar to
     the method in Kalish {\it et al} and also propose modifications of it (the WprevSeSp Poisson method proposed in this paper).

@@

    \item Minor issues:

    \begin{itemize}
        \item \textbf{2.2 Line 23-24: “where we define 0/0” seems unusual when this is typically taken as an indeterminate value. Clarify what is meant? The estimator in Equation 5 seems to be the Rogan-Gladen (1978) estimator with truncation in cases when the estimator falls outside the parameter range of [0, 1]?}

        We have adjusted the definition of the estimator to avoid defining 0/0 = 0. It is now presented as
        \begin{equation}
        \hat{\beta}^* \equiv 
        g(\hat{\theta}_1, \hat{\phi}_n, \hat{\phi}_p)
        \equiv 
        \left\{ 
        \begin{array}{ll}
        1 & \mbox{ if $\hat{\phi}_n < \hat{\phi}_p \leq \hat{\theta}_1$ }  \\
        \frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} & 
        \mbox{ if $\hat{\phi}_p > \hat{\theta}_1 \geq \hat{\phi}_n$ } \\
        0 & \mbox{ otherwise.} 
        \end{array}
        \right.
        \end{equation}

@@

        \item \textbf{2.2 Lines 24-32: It would be helpful for the unfamiliar reader to include more background on the melding method. For instance, what exactly is the definition of the confidence distribution? Why are the confidence distributions Beta for a binomial experiment?}

       We have added more background on the melding method, giving an intuitive definition of the confidence distribution (and referencing the more formal modern definition).
       We also now give some insight into why the lower and upper confidence distributions for the binomial are beta distributions.

@@

        \item \textbf{As a formatting note, the paper could be much more concise if (a) many of the figures were moved to appendices, and (b) fewer lines are used for equations, e.g., the definition of the Lang-Reiczigel interval in Section 2.2.}

        We have adjusted the some of the presentation in Sections 2.2 and 2.5.2  to reduce the lines used.

@@

        We have clarified this in the text:

        \begin{eqnarray*}
        \textrm{var}_P \left(\hat{\beta} \right) & = & \textrm{var}_P \left(  \frac{1}{n}  \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ I_{ij}  Y_j}{N P_j} \right)  \\
        & = &    \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ \textrm{var}_P( I_{ij})  Y_j^2}{n^2 N^2 P_j^2}  \\
        & = &    \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ \textrm{var}_P( I_{ij})  Y_j}{n^2 N^2 P_j^2}  \\
        & = &    \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{   Y_j}{n^2 N^2 P_j}.
        \end{eqnarray*}

        \item \textbf{There are several typographical errors that distract the reader. The manuscript should be reread with this attention to detail in mind. Some instances: 2.3 Line 52: “the wsPoison method”; Section 5: “Further worked is needed”; the inconsistency about the assessment of wsPoisson in the simulations; etc.}

        We have corrected a the errors described here and several others found upon further review.

### 2023-02-01 PrevAdjSurvey.tex
fix typos

\abstract[Abstract]{We present several related methods for creating confidence intervals to assess disease prevalence in variety of survey sampling settings. These include simple random samples with imperfect tests, weighted sampling with perfect tests, and weighted sampling with imperfect tests, with the first two settings considered special cases of the third. Our methods use survey results and measurements of test sensitivity and specificity to construct melded confidence intervals. We demonstrate that our methods appear to guarantee coverage in simulated settings, while competing methods are shown to achieve much lower than nominal coverage in some settings, especially when overall prevalence is very low. In other settings, our methods are shown to be overly conservative. We apply our method to a seroprevalence survey of SARS-CoV-2 in undiagnosed adults in the United States between May and July 2020.}

\keywords{confidence distributions, seroprevalence, survey sampling, weighted sampling}

@@

Estimating and quantifying uncertainty for disease prevalence is a standard task in epidemiology.
For rare events, these estimates are highly sensitive to misclassification \cite{hemenwaySelfDefense}, making adjustments for sensitivity and specificity critically important.
While estimating prevalence (or any event proportion in a population) in complex surveys and adjusting estimates for misclassification have been well studied separately, performing both of these tasks simultaneously remains relatively unexplored.
Recent overviews of methods for estimating prevalence in surveys without misclassification are provided by Dean and Pagano\cite{Dean:2015} and Franco, et al\cite{franco2019}.
For  simple random sample surveys with imperfect sensitivity and specificity, Lang and Reiczigel\cite{Lang:2014} proposed an approximate method that performed well in simulations. Recent work by DiCiccio, et al \cite{DiCi:2021} and Cai et al \cite{Cai:2020} study both valid (i.e., exact) and approximate methods. Their valid methods use test inversion and the adjustment of Berger and Boos \cite{Berg:1994}, while their approximation methods use the bootstrap with the test inversion approach. 
Fewer methods are available for for constructing frequentist confidence intervals for prevalence estimates from complex surveys while adjusting for sensitivity and specificity.
Kalish et al\cite{Kali:2021} developed one such method that is closely related to one of the methods presented here, but that method's properties were not studied.
Cai et al \cite{Cai:2020} (see also discussion in DiCiccio et al \cite{DiCi:2021}) modify their approximation approach to allow sample weights, but it assumes that the number of counts of events within the strata are large (see their Remark 4).  Thus, it would not apply to a weighted survey method where each individual their own weight. 
Another recent advancement is the method developed by Rosin et al \cite{rosin2021estimating} that 
 makes use of asymptotic normal approximations which reduce to the Wald interval when sensitivity and specificity are perfect.
This problem has also previously been addressed in Bayesian literature, recently by Gelman and Carpenter\cite{GelmanBayes}.

We work up to our ultimate goal in stages.
First, in Section~\ref{sec:srs-imperfect}, we propose confidence intervals for simple random samples where prevalence is assessed with an assay with imperfect sensitivity and/or specificity.
Next, in Section~\ref{sec:weight-perfect}, we present confidence intervals for weighted samples where prevalence is assessed with an assay without misclassification.
In Section~\ref{sec:weight-imperfect}, we combine these methods to create confidence intervals for weighted samples where prevalence is assessed with an assay with imperfect sensitivity and specificity.
Because the combined method reduces to one of the first two methods as a special case, we can think of the first two stages as testing the combined method in those cases.  Finally, in Section~\ref{sec:complex-surveys} we show how certain complex surveys may fit into the format for our new method.
Our new method is designed to guarantee coverage in all situations.

In simulations we compare our method to established frequentist competitors and  show through simulations that it beats the best of those in each of the three stages with respect to guaranteeing coverage.
However, in some simulated settings, our proposed methods are overly conservative, while competitor methods maintain closer to nominal coverage.
We did not include in our simulations the new methods that have been developed in response to the COVID-19 pandemic and are not yet in print in peer reviewed journals \cite{Cai:2020,DiCi:2021,rosin2021estimating}.
The exact method of DiCiccio, et al \cite{DiCi:2021} would guarantee coverage, although applying it to a survey with a large number of strata would be ``computationally expensive'', and it has not been applied to surveys using post-stratification weighting. In contrast, our new method can very tractable in those situations.

@@

To introduce notation, consider first the stratified simple random sample.
Suppose we have a population partitioned into   \( K \) strata, with \( N_1, N_2, \ldots, N_K \) individuals in the  K strata of the population.
We sample \( n_1, n_2, \ldots, n_K \) individuals via a simple random sample from each of the \( K \)  strata to have an assay performed to determine who has a disease.
Let \( X_i \) be the number of positive results from an assay performed on the \( n_i \) individuals from stratum \( i \) and assume \( X_i \sim \operatorname{Binomial}(n_i, \theta_i) \), where \( \theta_i \) is the population frequency of positive results for assays performed on individuals from stratum \( i \).
Similarly, let \( X_i^* \) be the unobserved true number of people with the disease among the \( n_i \) individuals from stratum  \( i \) and assume \( X_i^* \sim \operatorname{Binomial}(n_i, \theta_i^*) \), where \( \theta_i^* \) is the population frequency of cases in stratum \( i \).
In the case of a perfect assay, \( \theta_i = \theta_i^* \).

@@

We can relate $\theta_i$ and $\theta_i^*$ using the sensitivity ($\phi_p$)  and specificity (1-$\phi_n$) of the assay, 
where  $\phi_p$ and $\phi_n$  are the proportion of positive assays from a population of  positive controls (i.e., individuals known to have the disease) and 
negative controls (i.e., individuals known to be  without the disease), respectively. Then
$\theta_i = \phi_p \theta_i^* + \phi_n (1-\theta_i^*)$, or equivalently,  
\begin{eqnarray*}
\theta_i^* & = & \frac{ \theta_i - \phi_n }{\phi_p - \phi_n},
\end{eqnarray*}
and we have
\begin{align}
\begin{split}
  \beta^*   =&   \sum_{i=1}^K w_i \theta_i^* 
            =  \sum_{i=1}^K w_i \left( \frac{\theta_i - \phi_n}{\phi_p - \phi_n} \right) \\
            =&   \frac{\sum_{i=1}^K w_i \theta_i}{\phi_p - \phi_n} - \frac{\phi_n \sum_{i=1}^K w_i}{\phi_p - \phi_n} 
            =   \frac{\sum_{i=1}^K w_i \theta_i}{\phi_p - \phi_n} - \frac{\phi_n}{\phi_p - \phi_n}
            \label{eq:long-beta}
\end{split}
\end{align}

@@

This estimator serves as an important basis for developing confidence intervals in this work.
Section~\ref{sec:srs-imperfect} is concerned with confidence intervals for  \( \beta^* \) in the case where \( K = 1 \), \( \phi_n > 0 \), \( \phi_p < 1 \), i.e. estimating prevalence from a simple random sample with an imperfect assay.
Section~\ref{sec:weight-perfect} is concerned with confidence intervals for  \( \beta^* \) in the case where \( K > 1 \), \( \phi_n = 0 \), \( \phi_p = 1 \), i.e. estimating prevalence from a weighted sample with a perfect assay.
Section~\ref{sec:weight-imperfect} is concerned with confidence intervals for  \( \beta^* \) in the case where \( K > 1 \), \( \phi_n > 0 \), \( \phi_p < 1 \), i.e. estimating prevalence from a weighted sample with an imperfect assay.

@@

First, we consider the scenario where \( K = 1 \), \( \phi_n > 0 \), and \( \phi_p < 1 \).
We develop a confidence interval for the population prevalence, \( \beta^* \).
When \( K = 1 \), the estimand in Equation~\ref{eq:long-beta} becomes $\beta^* = (\theta_1 - \phi_n)/(\phi_p-\phi_n)$. We have $\phi_p > \phi_n$ for any useful assay, and since the sample is a mixture of individuals with and without the disease of interest, $\phi_p \geq \theta_1 \geq \phi_n$. The estimator of $\beta^*$ is 
%in Equation~\ref{eq:betastarhat} becomes

\begin{equation}
\hat{\beta}^* \equiv 
g(\hat{\theta}_1, \hat{\phi}_n, \hat{\phi}_p)
\equiv 
\left\{ 
\begin{array}{ll}
1 & \mbox{ if $\hat{\phi}_n < \hat{\phi}_p < \hat{\theta}_1$ }  \\
\frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} & 
\mbox{ if $\hat{\phi}_p > \hat{\theta}_1 \geq \hat{\phi}_n$ } \\
0 & \mbox{ otherwise.} 
\end{array}
\right.
\label{eq:srs-beta-est}
\end{equation}
% Damon, that definition is arbitrary, it is just used so that

To create a confidence interval for \( \hat{\beta}^* \), we use a generalization of the melding method \cite{FayP:2015}, which makes use of lower and upper confidence distributions on functions of independent estimators to account for variability in \( \hat{\theta}_1 \), \( \hat{\phi}_n \), and \( \hat{\phi}_p \). Confidence distributions are frequentist estimators of a parameter, which can be used similarly to the bootstrap or posterior distributions. Formally, a confidence distribution is a function \(H_{n}(\cdot)=H_{n}(\mathbf{x}, \cdot)\) on \(\mathcal{X} \times \Theta \rightarrow[0,1]\), where \( \Theta \) is the parameter space of the parameter of interest (\( \theta \)) and \( \mathcal{X} \) is the sample space corresponding to sample data \(\mathbf{x}=\left\{x_{1}, \ldots, x_{n}\right\}\), which has two properties: (i) For each \(\mathbf{x} \in \mathcal{X}, H_{n}(\cdot)\) is a cumulative distribution function on \(\Theta \). (ii) At the true parameter value \(\theta=\theta_{0}, H_{n}\left(\theta_{0}\right) \equiv H_{n}\left(\mathbf{x}, \theta_{0}\right)\), as a function of the sample \(\mathbf{x}\), follows the uniform distribution \(U[0,1]\) \cite{Xie2013}.

The lower and upper confidence distributions are used with discrete responses to ensure the validity of the resulting inferences, and for the binomial case they are equivalent to the posterior distributions that result from using well-calibrated null preference priors \cite{Fay2021}.

Each estimated component in Equation~\ref{eq:srs-beta-est} is a binomial probability parameter.
For each of these, we use distributions associated with  the exact binomial confidence interval.
For a binomial experiment with \( x \) successes out of \( n \) trials, the lower confidence distribution is \( \operatorname{Beta}(x, n - x + 1) \) with associated random variable \( B^L \), and the upper confidence distribution  is \( \operatorname{Beta}(x + 1, n - x)\) with random variable \( B^U \), where for $a>0$ we let \( \operatorname{Beta}(0,a) \) and \( \operatorname{Beta}(a,0) \) be point masses at 0 and 1, respectively.
Let \( q(a, W) \) be the \( a \)th quantile of a random variable \( W \). Then the exact \( 1 - \alpha \)\% central confidence interval of Clopper-Pearson\cite{10.1093/biomet/26.4.404} for the binomial parameter is 
\begin{equation}
\left\{ q \left( \frac{\alpha}{2}, B^L \right), q \left( 1 - \frac{\alpha}{2}, B^U, \right) \right\}.
\label{eq:C-P}
\end{equation}

Fay et al \cite{FayP:2015} proposed a method for obtaining confidence intervals for functions of two parameters that are monotonic within the allowable range  for each parameter given the other is fixed. Here we generalize that to $\beta^*$, which is a function of 3 parameters. When $1 \geq \phi_p > \theta_1 > \phi_n \geq 0$ then $\beta^*$ is monotonically increasing in $\theta_1$, monotonically decreasing in $\phi_p$, and monotonically decreasing in $\phi_n$.
For an assessment of monotonicity in other scenarios see Appendix~\ref{monotonicity}.
Then the \( 1-\alpha \)\% confidence interval for \( \beta^* \) is

>>>>

\abstract[Abstract]{There are established methods for estimating disease prevalence with associated confidence intervals for complex surveys with perfect assays, or simple random sample surveys with imperfect assays.
We develop and study methods for the complicated case of complex surveys with imperfect assays.
The new methods use the melding method to combine gamma intervals for directly standardized rates and established adjustments for imperfect assays by estimating sensitivity and specificity.
One of the new methods appears to have at least nominal coverage in all simulated scenarios.
We compare our new methods to established methods in special cases (complex surveys with perfect
assays or simple surveys with imperfect assays).
In some simulations, our methods appear to guarantee coverage, while competing methods have much lower than nominal coverage, especially when overall prevalence is very low.
In other settings, our methods are shown to have higher than nominal coverage.
We apply our method to a seroprevalence survey of SARS-CoV-2 in undiagnosed adults in the United States between May and July 2020.}

\keywords{confidence distributions, melding confidence intervals, seroprevalence, survey sampling, weighted sampling}

@@

Estimating and quantifying uncertainty for disease prevalence is a standard task in epidemiology.
For rare events, these estimates are highly sensitive to misclassification,\cite{hemenwaySelfDefense} making adjustments for sensitivity and specificity critically important.
While estimating prevalence (or any event proportion in a population) in complex surveys and adjusting estimates for misclassification have been well studied separately, performing both of these tasks simultaneously remains relatively unexplored. This paper fills that gap by studying estimates and confidence intervals for prevalence from complex surveys with misclassification.
We develop a new tractable confidence interval procedure designed to guarantee coverage.
Our confidence interval combines three statistical methods: (1) the gamma confidence interval for directly standardized rates is applied to the apparent prevalence\cite{FayF:1997}
and (2) standard misclassification adjustments to that apparent prevalence for sensitivity and specificity \cite{Roga:1978} are used together with (3) the melding method, which allows combination of confidence intervals for different parameters.\cite{FayP:2015}
We show by simulation only (there are no proofs of guaranteed coverage) that, with a complex survey with low prevalence and misclassification, our method appears to have at least nominal coverage.
Even in special cases (e.g., simple random samples with imperfect assays, or weighted samples with perfect assays) where there are existing methods, our new method has at least nominal simulated coverage. while some of the tractable existing methods may under-cover.
The cost for apparently achieving nominal coverage is that our intervals may be quite wide in some situations.

Recent overviews of confidence interval procedures for prevalence in surveys without misclassification are provided by Dean and Pagano\cite{Dean:2015} and Franco, et al.\cite{franco2019}
For simple random sample surveys with imperfect sensitivity and specificity, Lang and Reiczigel\cite{Lang:2014} proposed an approximate confidence interval that performed well in simulations. Recent work by DiCiccio, et al \cite{DiCi:2021} and Cai et al\cite{Cai:2020} study both valid (i.e., exact) and approximate intervals. Their valid intervals use test inversion and the adjustment of Berger and Boos,\cite{Berg:1994} while their approximation intervals use the bootstrap with the test inversion approach.
Fewer methods are available for for constructing frequentist confidence intervals for prevalence estimates from complex surveys while adjusting for sensitivity and specificity.
Kalish et al\cite{Kali:2021} developed one such method that is closely related to one of the methods presented here, but that method's properties were not studied.
Cai et al\cite{Cai:2020} (see also discussion in DiCiccio et al\cite{DiCi:2021}) modify their approximation approach to allow sample weights for strata or individual specific weights.
Another recent advancement is the method developed by Rosin et al\cite{rosin2021estimating} that makes use of asymptotic normal approximations which reduce to the Wald interval when sensitivity and specificity are perfect.
This problem has also previously been addressed in Bayesian literature, recently by Gelman and Carpenter. \cite{GelmanBayes}

We work up to our ultimate goal in stages.
First, in Section~\ref{sec:srs-imperfect}, we propose confidence intervals for simple random samples where prevalence is assessed with an assay with imperfect sensitivity and/or specificity.
Next, in Section~\ref{sec:weight-perfect}, we present confidence intervals for weighted samples where prevalence is assessed with an assay without misclassification.
In Section~\ref{sec:weight-imperfect}, we combine these methods to create confidence intervals for weighted samples where prevalence is assessed with an assay with imperfect sensitivity and specificity.
Because the combined method reduces to one of the first two methods as a special case, we can think of the first two stages as testing the combined method in those cases.
Finally, in Section~\ref{sec:complex-surveys} we show how certain complex surveys may fit into the format for our new method.

In simulations we compare our method to established frequentist competitors and show through simulations that it beats the best of those in each of the three stages with respect to guaranteeing coverage.
However, in some simulated settings, our proposed methods are overly conservative, meaning that they demonstrate higher than nominal coverage, while competitor methods maintain closer to nominal coverage.
We did not include in our simulations some recent methods that have been developed in response to the COVID-19 pandemic.\cite{Cai:2020,DiCi:2021,rosin2021estimating}
The exact method of DiCiccio, et al\cite{DiCi:2021} would guarantee coverage, although applying it to a survey with a large number of strata would be ``computationally expensive,'' and it has not been applied to surveys using post-stratification weighting. In contrast, our new method can very tractable in those situations.

@@

To introduce notation, consider first the stratified simple random sample.
Suppose we have a population partitioned into \( K \) strata, with \( N_1, N_2, \ldots, N_K \) individuals in the \( K \) strata of the population.
We sample \( n_1, n_2, \ldots, n_K \) individuals via a simple random sample from each of the \( K \) strata to have an assay performed on each individual to determine who has the disease.
Let \( X_i \) be the number of positive results from an assay performed on the \( n_i \) individuals from stratum \( i \) and assume \( X_i \sim \operatorname{Binomial}(n_i, \theta_i) \), where \( \theta_i \) is the population frequency of positive results for assays performed on individuals from stratum \( i \).
Similarly, let \( X_i^* \) be the unobserved true number of people with the disease among the \( n_i \) individuals from stratum \( i \) and assume \( X_i^* \sim \operatorname{Binomial}(n_i, \theta_i^*) \), where \( \theta_i^* \) is the population frequency of cases in stratum \( i \).
In the case of a perfect assay, \( \theta_i = \theta_i^* \).

@@

We can relate $\theta_i$ and $\theta_i^*$ using the sensitivity ($\phi_p$) and specificity (1-$\phi_n$) of the assay,
where $\phi_p$ and $\phi_n$ are the proportion of positive assays from a population of positive controls (i.e., individuals known to have the disease) and
negative controls (i.e., individuals known to be without the disease), respectively. Then
$\theta_i = \phi_p \theta_i^* + \phi_n (1-\theta_i^*)$, or equivalently,\cite{Roga:1978}
\begin{eqnarray*}
\theta_i^* & = & \frac{ \theta_i - \phi_n }{\phi_p - \phi_n},
\end{eqnarray*}
and we have
\begin{align}
\begin{split}
  \beta^*   =&   \sum_{i=1}^K w_i \theta_i^*
            =  \sum_{i=1}^K w_i \left( \frac{\theta_i - \phi_n}{\phi_p - \phi_n} \right) \\
            =&   \frac{\sum_{i=1}^K w_i \theta_i}{\phi_p - \phi_n} - \frac{\phi_n \sum_{i=1}^K w_i}{\phi_p - \phi_n}
            =   \frac{\sum_{i=1}^K w_i \theta_i}{\phi_p - \phi_n} - \frac{\phi_n}{\phi_p - \phi_n}
            \label{eq:long-beta}
\end{split}
\end{align}

@@

This estimator serves as an important basis for developing confidence intervals in this work.
Section~\ref{sec:srs-imperfect} is concerned with confidence intervals for \( \beta^* \) in the case where \( K = 1 \), \( \phi_n > 0 \), \( \phi_p < 1 \), i.e., estimating prevalence from a simple random sample with an imperfect assay.
Section~\ref{sec:weight-perfect} is concerned with confidence intervals for \( \beta^* \) in the case where \( K > 1 \), \( \phi_n = 0 \), \( \phi_p = 1 \), i.e., estimating prevalence from a weighted sample with a perfect assay.
Section~\ref{sec:weight-imperfect} is concerned with confidence intervals for \( \beta^* \) in the case where \( K > 1 \), \( \phi_n > 0 \), \( \phi_p < 1 \), i.e., estimating prevalence from a weighted sample with an imperfect assay.

@@

First we consider the scenario where \( K = 1 \), \( \phi_n > 0 \), and \( \phi_p < 1 \).
We develop a confidence interval for the population prevalence, \( \beta^* \).
When \( K = 1 \), the estimand in Equation~\ref{eq:long-beta} becomes $\beta^* = (\theta_1 - \phi_n)/(\phi_p-\phi_n)$. We have $\phi_p > \phi_n$ for any useful assay, and since the sample is a mixture of individuals with and without the disease of interest, $\phi_p \geq \theta_1 \geq \phi_n$. The estimator of $\beta^*$ is
%in Equation~\ref{eq:betastarhat} becomes

\begin{equation}
\hat{\beta}^* \equiv
g(\hat{\theta}_1, \hat{\phi}_n, \hat{\phi}_p)
\equiv
\left\{
\begin{array}{ll}
1 & \mbox{ if $\hat{\phi}_n < \hat{\phi}_p \leq \hat{\theta}_1$ }  \\
\frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} &
\mbox{ if $\hat{\phi}_p > \hat{\theta}_1 \geq \hat{\phi}_n$ } \\
0 & \mbox{ otherwise.}
\end{array}
\right.
\label{eq:srs-beta-est}
\end{equation}
% Damon, that definition is arbitrary, it is just used so that

To create a confidence interval for \( \hat{\beta}^* \), we use a generalization of the melding method, \cite{FayP:2015} which makes use of lower and upper confidence distributions on functions of independent estimators to account for variability in \( \hat{\theta}_1 \), \( \hat{\phi}_n \), and \( \hat{\phi}_p \).
Before describing the melding method, we briefly review confidence distributions.

Confidence distributions are frequentist estimators of a parameter, which can be used similarly to the bootstrap or posterior distributions.
For continuous responses (and asymptotically for discrete responses), one can formally define confidence distributions without relying on previously derived confidence interval procedures,\cite{Xie2013} but for intuition with discrete responses, it is easier to derive confidence distributions the classical way, i.e., directly from confidence interval procedures.
For discrete responses there are two confidence distributions (the lower and upper ones), used to ensure validity of the resulting inferences.
Under the classical derivation, we can create random variables associated with the lower and upper confidence distributions from two one-sided, nested, confidence interval procedures, where for a nested confidence interval procedure, the $(1-\alpha_1)$ interval is a subset of the $(1-\alpha_2)$ interval whenever $(1-\alpha_1) \leq (1-\alpha_2)$.
Denote those one-sided intervals by $[L({\bf x},1-\alpha), \infty)$ and $(-\infty, U({\bf x},1-\alpha)]$, which are defined for any observed data ${\bf x}$, and $(1-\alpha) \in (0,1)$.
For fixed ${\bf x}$, define the lower and upper confidence distribution random variables as $L({\bf x}, A)$ and $U({\bf x},B)$, where $A$ and $B$ are independent uniform random variables.
Then a $100(1-\alpha)\%$ central confidence interval has the $(\alpha/2)$th quantile of $L({\bf x}, A)$ as the lower limit, and the $(1-\alpha/2)$th quantile of $U({\bf x},B)$ as the upper limit.

Because each estimated component in Equation~\ref{eq:srs-beta-est} is a binomial probability parameter, we now focus on the confidence distributions associated with the exact binomial confidence interval.
For a binomial experiment with \( x \) successes out of \( n \) trials, the lower confidence distribution is \( \operatorname{Beta}(x, n - x + 1) \) with associated random variable \( B^L \), and the upper confidence distribution is \( \operatorname{Beta}(x + 1, n - x)\) with random variable \( B^U \), where for $a>0$ we let \( \operatorname{Beta}(0,a) \) and \( \operatorname{Beta}(a,0) \) be point masses at 0 and 1, respectively.
This result comes from the relationship between the binomial and beta distributions, namely $\mathrm{Pr}[X \leq x] = \mathrm{Pr}[B > \theta]$, where $B \sim \operatorname{Beta}(x + 1, n - x)$ for $x \in \left\{ -1,0, 1, \ldots, n \right\}$ (see e.g., \cite[Section~2]{Blyth1986}, \cite[Section~S2]{Fay2021}).
Additionally, in the binomial case, the lower and upper confidence distributions are equivalent to
the posterior distributions that result from using well-calibrated null preference priors.\cite{Fay2021}
Let \( q(a, W) \) be the \( a \)th quantile of a random variable \( W \). Then the exact \( 1 - \alpha \)\% central confidence interval of Clopper-Pearson\cite{10.1093/biomet/26.4.404} for the binomial parameter is
\begin{equation}
\left\{ q \left( \frac{\alpha}{2}, B^L \right), q \left( 1 - \frac{\alpha}{2}, B^U, \right) \right\}.
\label{eq:C-P}
\end{equation}
